### 2009-11-24 thesis/SensorMLOnSenseTile/trunk/thesis/SensorMLonSenseTileThesis.tex
add static diagram

@@

@@

@@

\chapter{Design}
High level design
\section{SenseTile Web Service}

DataProducer - use PacketInput stream to access SenseTile observation packets.

@@

System reads packets and averages them for 1 second.

@@

\section{SensorML generation tool}

SensorML to BON mapping

BON to Java

Instantiate Java classes with data

Walk Java class and generate sensorml.

@@

\chapter{Results}

@@

\chapter{References}

@@

\newpage
\begin{thebibliography}{99}
\bibitem{SensoMLref}Open Geospatial Consortium Inc., OpenGIS Sensor Model Language (SensorML) Implementation Specification, 2007
\bibitem{BONref}Kim Waldén and Jean-Marc Nerson , "Seamless Object-Oriented Software Architecture", 1995
\end{thebibliography}
\label{endpage}

>>>>

\subsection{Sensor Networks}
\subsection{BON}
\subsection{Sensorml}
reference chapter
\subsection{WebService}
\subsection{JIBX}

@@

Naming rules inputs and outputs - allow more generic handling of implementation classes.

Processed verus raw data.

@@

DataArray

@@

\chapter{Design}
High level design
\section{SenseTile Web Service}
 \begin{figure}
\scalebox{0.65}{\includegraphics{sensetile_static_diagam.png}}
\caption{SenseTile Static Diagram}\label{fig:sensetile_static_diagam.png}
\end{figure}
DataProducer - use PacketInput stream to access SenseTile observation packets.

@@

System reads packets and averages them for every configurable seconds. Defalut 1.

@@

\newpage
\section{SensorML generation tool}

BON to SensorML mapping.

Features to be elements or attributes.

Name rule suffix "Attrib" to make it an attribute.

List handling - convention for mapping.

Java binding wth JIBX  generate sensorml.

Simple xml file with Sensor metadata.

Naming rules allow connection of inputs and outputs
in sensorML processes.

@@

RMI used between DataProvider and DataProducer.
\chapter{Results}

@@

\chapter{References}
\newpage
\begin{thebibliography}{99}
\bibitem{SensoMLref}Open Geospatial Consortium Inc., OpenGIS Sensor Model Language (SensorML) Implementation Specification, 2007
\bibitem{BONref}Kim Waldén and Jean-Marc Nerson , "Seamless Object-Oriented Software Architecture", 1995
\end{thebibliography}
\label{endpage}

@@
